### 2014-03-31 paper/tubes.tex
put in bjoern comments

As mentioned, pipe design is not trivial.  Independent pipes cannot intersect lest their contents be unintentionally mixed.  Pipes' bending energy needs to be minimized to allow for easy insertion of media post-print.  Pipes in general need to avoid the surface of objects to prevent fluid leakage when printed by hobbyist-grade machines.  Finally, for designing pipes that follow a user-specified path, we must ensure certain characteristics of that path (e.g., that the path is connected).

@@

Designing objects which, for example, are touch sensitive in particular areas or need to integrate with existing electronics, requires precise location and sizing of pipe endpoints.  The interior of these pipes should have as large a bending radius as possible so that post-print insertion of solid or viscous media (like wire or paint) is easier.

@@

Given our initial routing, we create a rod of the same length.  To allow for easiest insertion of media post-print, our physical simulation step minimizes the bend radius of the generated rod.  In order to force our simulated rod away from the surface of the mesh, we create ``wind'' pushing inward from the exterior of the mesh.  This wind keeps the resulting pipe away from the surface. \valkyrie{Ryan: How does it actually work?}

@@

\subsubsection{Pipes with Non-Round Endpoints}
\valkyrie{this section can probably be scrapped, along with Figure \ref{fig:meshmixer-endpoint}.}
Although start and end radius of pipes is configurable, our tool does not explicitly allow makers to design the \emph{shape} of their pipes' endpoints.  However, the larger Meshmixer package does allow brushing arbitrary shapes onto the surface and extruding them inward, as in Figure \ref{fig:meshmixer-endpoint}.  This technique can be used to create specially-shaped touch pads or to recess the footprint of an electronic component for it to sit flush with the object's surface.

@@

Neon signs, as in Figure \ref{fig:tool-process-interior}(d), require a single long path that passes through many desired edges: for example, in our UIST sign, the path must pass through all the edges that comprise the word ``UIST''.  To allow makers to create novel neon signs, as well as similar objects that require design of the pipe's interior path (for example the maze in Figure \ref{fig:maze}), we built a tool which leverages graph theory to generate this single long path.

@@

\subsubsection{Routing}
\tovi{Still too long....}
In graph theory, a semi-Eulerian graph is one which has exactly two edges of odd degree.  This kind of graph supports an Euler tour: a path that touches every edge exactly once, beginning and ending at the two nodes of odd degree (in this case, the user-selected start and end nodes).  To allow for a single path through a pipe for post-print media insertion, we need to find a semi-Eulerian graph for which a user's input graphics are a subset, and subsequently find an Euler tour on that graph.

@@

All cylinders generated are joined into a large rod.  This rod is voxelized, along with the original mesh.  These two voxel grids are subtracted, and the result is re-meshed and smoothed.  When a user desires to cap the ends of her pipes, we create a sphere of the same radius as each endpoint whose center is the same as the endpoint.  We intersect this sphere with the original mesh, then intersect this partial-sphere mesh with a shell of the original mesh.  This gives us a voxel subgrid of the thickness of cap we desire (the same as the shell's thickness) which is located only in the region of the tube end.  During subtraction, we preserve this subgrid. \valkyrie{maybe need a figure?}

Unfortunately, because we use voxelization as a part of our subtraction operation, our models can accumulate error when many pipes are created in sequence (see Figure \ref{fig:voxelize}).  This problem could be solved by performing a multi-pipe operation; fewer rounds of voxelization and re-meshing lead to lower error.  This multi-pipe operation would also lead to a more globally optimal pipe routing.

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/voxelize-fail.png}
\caption{After repeated pipe creation, the mesh containing these pipes, which were not originally intersecting, accumulated sufficient error to open the pipes into each other.}
\label{fig:voxelize}
\end{figure}

@@

The physical fabrication process used by different machines gives rise to differing strategies for avoiding support material or easing its removal.  The two machines we used to create our example objects were the Objet Connex 260 and the Makerbot Replicator 2.

>>>>

Pipe design is not trivial.  Independent pipes cannot intersect lest their contents be unintentionally mixed.  Pipes' bending energy needs to be minimized to allow for easy insertion of media post-print.  Pipes in general need to avoid the surface of objects to prevent fluid leakage when printed by hobbyist-grade machines.  Finally, for designing pipes that follow a user-specified path, we must ensure certain characteristics of that path (e.g., that the path is connected).

@@

\bjoern{Hits section mentions a* three times, ech time with a little more detail than before. An probably cut this to two times as a general strategy: once in the overview, then a second time in detail.}
Designing objects which, for example, are touch sensitive in particular areas or need to integrate with existing electronics, requires precise location and sizing of pipe endpoints.  The interior of these pipes should have as large a bending radius as possible so that post-print insertion of solid or viscous media (like wire or paint) is easier.

@@

Given our initial routing, we create a rod of the same length.  To allow for easiest insertion of media post-print, our physical simulation step minimizes the bend radius of the generated rod.  In order to force our simulated rod away from the surface of the mesh, we create ``wind'' pushing inward from the exterior of the mesh.  This wind keeps the resulting pipe away from the surface. \valkyrie{Ryan: How does it actually work?} \bjoern{Need much more detail here or a reference to a previously published technique}

@@

\subsubsection{Pipes with Non-Round Endpoints}
\valkyrie{this section can probably be scrapped, along with Figure \ref{fig:meshmixer-endpoint}.}
\bjoern{Replace with a single sentence: combining pipe routing with other existing mesh modification operations like extrusions enables users to create custom ...}
Although start and end radius of pipes is configurable, our tool does not explicitly allow makers to design the \emph{shape} of their pipes' endpoints.  However, the larger Meshmixer package does allow brushing arbitrary shapes onto the surface and extruding them inward, as in Figure \ref{fig:meshmixer-endpoint}.  This technique can be used to create specially-shaped touch pads or to recess the footprint of an electronic component for it to sit flush with the object's surface.

@@

\bjoern{Replace specific with more general category: pipes where interior path layout matters}
Neon signs, as in Figure \ref{fig:tool-process-interior}(d), require a single long path that passes through many desired edges: for example, in our UIST sign, the path must pass through all the edges that comprise the word ``UIST''.  To allow makers to create novel neon signs, as well as similar objects that require design of the pipe's interior path (for example the maze in Figure \ref{fig:maze}), we built a tool which leverages graph theory to generate this single long path.

@@

\subsubsection{Routing}
\tovi{Still too long....}
\bjoern{Need this explanation above so readers don't wonder what Euler tours are

Agree with Tovi that this can be condensed}
In graph theory, a semi-Eulerian graph is one which has exactly two edges of odd degree.  This kind of graph supports an Euler tour: a path that touches every edge exactly once, beginning and ending at the two nodes of odd degree (in this case, the user-selected start and end nodes).  To allow for a single path through a pipe for post-print media insertion, we need to find a semi-Eulerian graph for which a user's input graphics are a subset, and subsequently find an Euler tour on that graph.

@@

All cylinders generated are joined into a large rod.  This rod is voxelized, along with the original mesh.  These two voxel grids are subtracted, and the result is re-meshed and smoothed.  \bjoern{ rewrite When a user desires to cap the ends of her pipes, we create a sphere of the same radius as each endpoint whose center is the same as the endpoint.  We intersect this sphere with the original mesh, then intersect this partial-sphere mesh with a shell of the original mesh.}  This gives us a voxel subgrid of the thickness of cap we desire (the same as the shell's thickness) which is located only in the region of the tube end.  During subtraction, we preserve this subgrid. \valkyrie{maybe need a figure?}

Unfortunately, because we use voxelization as a part of our subtraction operation, our models can accumulate error when many pipes are created in sequence (see Figure \ref{fig:voxelize}).  This problem could be solved with a higher voxel resolution, but it requires balancing computation time and precision.

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/voxelize-fail.png}
\caption{After repeated pipe creation, the mesh containing these pipes, which were not originally intersecting, accumulated sufficient error to open the pipes into each other. \bjoern{I don't understand this figure- probably requires multiple parts - ideal geometry and actual geometry}}
\label{fig:voxelize}
\end{figure}

@@

\bjoern{Argue first that we need processes to fabricate these hollow pipes- can do this by removing support material or never printing such material in the first place.}  \bjoern{Is section needs to bee written from a general standpoint first, and then our specific details second.}
The physical fabrication process used by different machines gives rise to differing strategies for avoiding support material or easing its removal.  The two machines we used to create our example objects were the Objet Connex 260 and the Makerbot Replicator 2.
